Dissertation draft

### 2023-07-22 Texfiles/Draft1.tex
More (bad) words

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[authoryear]{natbib}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{pdflscape}
\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\date{Lent 2023}
\title{Dissertation draft}
\author{Tobias Leigh-Wood}
\usepackage[letterpaper, margin=1.1in]{geometry}
\linespread{1.1}

@@

\section{Methodology and Econometric Strategy}

I first solve a modified retirement lifecycle model. The problem that retirees face is as follows.
Every period retirees solve:
\begin{equation*}
  V_{t}(a_{t}, y) = \underset{a_{t+1}, c_{t}}{\max} \{ u(c_{t}) + p_{t}B(a_{t+1}) + \beta(1-p_{t})V_{t+1}(a_{t+1}, y) \}
\end{equation*}
subject to their budget constraint
\begin{equation*}
  c_{t} =a_{
  t}(1 +r) -  a_{t+1} + y
\end{equation*}
where $a_{t}$ are asset holdings in time t, $y$ is constant income for all periods and . Income can come either
from state pensions, defined benefit pension plans or purchased annuities.
\begin{equation*}
  u(c_{t}) = \frac{c_{t}^{1 - \sigma}}{1 - \sigma}
\end{equation*} In some specifications retirees can leave bequests, I use the bequest function from
\cite{lockwood_red_2012}.
\begin{equation*}
  B(a_{t}) = \bigl( \frac{m}{1 - m} \bigr)^{\sigma}  \frac{(\frac{m}{1 - m}c_{0} + a_{t})^{(1 - \sigma)}}{1 - \sigma}
\end{equation*}
Where $b_{t}$ is the amount left at death, $m$ is a measure of bequest motive strength and $c_{0}$ is
a minimum amount of consumption that individuals want. \textbf{Check this}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[authoryear]{natbib}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{siunitx}
\newcolumntype{d}{S[
      input-open-uncertainty=,
      input-close-uncertainty=,
      parse-numbers = false,
      table-align-text-pre=false,
      table-align-text-post=false
    ]}
\usepackage{pdflscape}
\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\date{Lent 2023}
\title{Dissertation draft}
\author{Tobias Leigh-Wood}
\usepackage[letterpaper, margin=1.1in]{geometry}
\linespread{1.1}

@@

\begin{landscape}
    \input{tables/elsa_results_only_dc.tex}
\end{landscape}

Table \ref{tab:DcOnlyRes} shows the results of this specification on the various consumption indicators.
Column one has total monthly consumption as variable on the left hand side of the regression equation.
We can see that being in the treatment group is associated with £83 more a week in spending
overall across all categories of expenditure. This is not statistically significant using
robust standard errors (find a reference for the SE that I use). Being older at the time of interview
is also associated with lower consumption whilst those who retired later have lower consumption
because years since the start of retirement is associated with higher total consumption.

Columns 2 through 4 use food consumption as the outcome variable. Interestingly food consumption
in the house does not increase as a result of the policy reform but food out side the house does
increase. If individuals see their pension pot, that they previously could not access, as a
shock to their wealth, like winning the lottery, then we would the consumption basket to
include more goods that are perceived as luxuries. Likewise, consumption on clothing, shown in
column 4 increases as a result of the policy change.

I now run another specification which seeks to control for some of the cohort effect that
could be driving these results instead. As the financial characteristics in \ref{tab:sum_stats}
show, the treatment group has higher levels of wealth than the untreated group. To test
for cohort effects I add individuals who have a defined benefit pension pot into the model
and interact the policy change with a dummy for having a defined contribution pension pot.
This makes the coefficient of interest the interacted term, which shows us the difference
in the change in consumption between the DB and DC group. Since rules for defined benefit
pensions did not change under the pensions freedom act, this group can be seen as a natural counterfactual
group to judge the consumption of the defined contribution group against.

\section{Life cycle theory}

In the second part of the paper I first solve a modified retirement lifecycle model and then use data from the solved lifecycle
model
lifecycle consumption
. The problem that retirees face is as follows.
Every period retirees solve:
\begin{equation*}
    V_{t}(a_{t}, y) = \underset{a_{t+1}, c_{t}}{\max} \{ u(c_{t}) + p_{t}B(a_{t+1}) + \beta(1-p_{t})V_{t+1}(a_{t+1}, y) \}
\end{equation*}
subject to their budget constraint
\begin{equation*}
    c_{t} =a_{
    t}(1 +r) -  a_{t+1} + y
\end{equation*}
where $a_{t}$ are asset holdings in time t, $y$ is constant income for all periods and . Income can come either
from state pensions, defined benefit pension plans or purchased annuities.
\begin{equation*}
    u(c_{t}) = \frac{c_{t}^{1 - \sigma}}{1 - \sigma}
\end{equation*} In some specifications retirees can leave bequests, I use the bequest function from
\cite{lockwood_red_2012}.
\begin{equation*}
    B(a_{t}) = \bigl( \frac{m}{1 - m} \bigr)^{\sigma}  \frac{(\frac{m}{1 - m}c_{0} + a_{t})^{(1 - \sigma)}}{1 - \sigma}
\end{equation*}
Where $b_{t}$ is the amount left at death, $m$ is a measure of bequest motive strength and $c_{0}$ is
a minimum amount of consumption that individuals want. \textbf{Check this}
